Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-15 latex/main.tex
Update fig 1 caption
Closes #666

\begin{figure}[h]
\centering
\includegraphics[width=0.85\linewidth]{sc2ts_methodology}
\caption{
Schematic overview of sc2ts.
(A) Procedure to build an ARG by incrementally updating it with samples sorted by collection dates.
Sample 0 is used to initialize the ARG as the root.
Next, Sample 1 is attached, mapping mutations onto the new branch to explain it.
When Sample 4 is detected as a recombinant,
a node representing the recombination event is inserted with two edges connecting to its parents,
with Sample 4 itself attached to this node as its child.
The resulting ARG contains two local trees,
one on each side of the inferred breakpoint.
(B) Copying paths for Sample 4 inferred under the LS model
while allowing recombination ($k = 4$) or disallowing it ($k = 1000$).
}
\label{fig:methodology}
\end{figure}

@@

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
% FIXME: these samples are chosen randomly and so almost certainly do not
% belong to the correct quadrants.
A & \includegraphics[height=\cprheight]{static/causedby-ERR10306608.png}\\
B & \includegraphics[height=\cprheight]{static/causedby-ERR6760245.png}\\
C & \includegraphics[height=\cprheight]{static/causedby-SRR15864165.png}\\
D & \includegraphics[height=\cprheight]{static/causedby-SRR21087725.png}\\
\end{tabularx} 
\caption{Examples of problematic copying patterns. A-D are examples drawn from
the labelled quadrants in Figure~\ref{fig:recombinant_qc}.}
\label{fig:copying_pattern_examples}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.85\linewidth]{sc2ts_methodology}
\caption{
Schematic overview of sc2ts.
(A) Process to build an ARG by incrementally updating it with samples sorted by collection dates.
(B) The ARG resulting from the inference process.
Sample 0 is used to initialize the ARG as the root.
Next, Sample 1 is attached, mapping mutations onto the new branch to explain it.
When Sample 4 is detected as a recombinant,
a node representing the recombination event is inserted with two edges connecting to its parents,
with Sample 4 itself attached to this node as its child.
(C) Two local trees contained in the resulting ARG,
one on each side of the inferred breakpoint (A), which occurs at position 50.
The genomic coordinates of the segments inherited from different recombinant parents
are denoted by two half-open intervals (B).
(D) Copying paths for Sample 4 inferred under the LS model
while allowing recombination ($k = 4$) or disallowing it ($k = 1000$).
}
\label{fig:methodology}
\end{figure}

@@

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
% FIXME: these samples are chosen randomly and so almost certainly do not
% belong to the correct quadrants.
Q1 & \includegraphics[height=\cprheight]{static/causedby-ERR10306608.png}\\
Q2 & \includegraphics[height=\cprheight]{static/causedby-SRR15864165.png}\\
Q3 & \includegraphics[height=\cprheight]{static/causedby-ERR6760245.png}\\
Q4 & \includegraphics[height=\cprheight]{static/causedby-SRR21087725.png}\\
\end{tabularx}
\caption{Examples of problematic copying patterns. A-D are examples drawn from
the labeled quadrants in Figure~\ref{fig:recombinant_qc}.}
\label{fig:copying_pattern_examples}
\end{figure}
